Architectures and Open pNets

### 2018-02-09 2018-Arch-pNets/arch-pNets.tex
unification trial ...

@@

@@

$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
\AlgB$ is a guard, and the variables $x_j\in P$
are assigned the expressions $e_j\in \AlgE$.
If 
$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
		J}\rangle} s'\in \to $ then 
% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
\emph{sort} of
hole $j$.

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

>>>>

\paragraph{Unifying notations -- remarks}

@@

states looks ok, but initial state is $s_0$ in pnet and not in archi : $s^0$ . exponent 
position was removed from pnet because we found it complex with indexed set notation but 
could be ok.

@@

$\langle \alpha,~g,~e\rangle$,
where $\alpha \in\AlgA$ is a parameterised action, $g$ is a guard, and the variables 
$x_j\in \vars(s')$
are assigned the updates in $e$.
If 
$s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to $ then 
% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
		$\vars(\codom(e))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
		\vars(\dom(e))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

\end{itemize}
\end{definition}
\noteLH[]{}is dom and codom clear?
Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
%\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
%\emph{sort} of
%hole $j$.

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$. $g_k $ is a guard associated to the vector 
$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
